The Effects of Stellar Binarity on Transit Survey Occurrence Rates

### 2017-10-04 paper/ms.tex
add model_2_analysis scripts

To assess whether it is reasonable to take this limit, we want the mean
value of $X_\Gamma$, or the median, or else some other summary statistic.
Recall that all the terms in Eq.~\ref{eq:model2_xgamma_simple} are
random variables, and note that they are inter-dependent.
This latter fact impedes analytic progress.

Running a Monte Carlo simulation in which we fix the planet and primary star 
properties, draw the binary mass ratio from Eq.~\ref{eq:pdf_q_mag_limited}, 
and take 
the luminosity as $L\propto M^{3.5}$, we find 
a mean of $\langle X_\Gamma \rangle ={\bf VALUE HERE}$,
and a median of ${\rm median}(X_\Gamma) ={\bf VALUE HERE}$.
The distribution is shown in Figure BLAH.

>>>>

For the stellar population described in this model, with a mean light ratio 
$\langle \gamma_R \rangle \approx 0.27$, this limit is not strictly applicable.
To assess the importance of the error, we want the mean
value of $X_\Gamma$, or the median, or else some other summary statistic.
Recall that all the terms in Eq.~\ref{eq:model2_xgamma_simple} are
random variables, and note that they are inter-dependent.
This latter fact impedes us from analytically expressing these 
descriptive statistics.

Running a Monte Carlo simulation in which we fix the planet and primary star 
properties, draw the binary mass ratio from Eq.~\ref{eq:pdf_q_mag_limited}, 
and take 
the luminosity as $L\propto M^{3.5}$, we find 
a mean of 
\begin{equation}
\langle X_\Gamma \rangle =1.291\quad ({\rm Monte\ Carlo\ result}),
\end{equation}
and a median that is essentially the same.
This value is comparable to what one would guess using the analytic results 
for $\langle N_d \rangle / N_s$ to substitute $\beta$, and $\gamma_R$ to 
compute $f_{d1,c}$.
